A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-22 main.tex
Wrote on equivalence rules other than \QCsp.

The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \andalso
		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \andalso
		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[4mm]
		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \andalso
		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[4mm]
		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \andalso
		\infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \andalso
		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent} \andalso
		\caption{Tem Equivalence Rules}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}

>>>>

The equivalence of terms is defined in Figure \ref{fig:term-equivalence-rules}.
\QAbs, \QApp, \QTB, \QTBL, \QGen, \QIns, \QCsp\ are generated directly from the syntax of a term.
\QRefl, \QSym, \QTrans\ exist in order to make the term equivalence relation an equivalence relationship as with the type equivalence.
The rule \QBeta\ means when a term $M \longrightarrow_\beta M'$, $M$ is equivalent to $M'$.
\QTBLTB and \QLambda are corresponding to $\longrightarrow_\blacklozenge$ and $\longrightarrow_\Lambda$, respectively.

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \\[2mm]
		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[2mm]
		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[2mm]
		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
		\caption{Tem Equivalence Rules}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}
